---
title: "hana Marketing Conversion and Trends "
resource_files:
- inc/funnel_data.RData
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    theme: readable
    logo: inc/hana_logo_small.png
    css: inc/corp-styles.css
    includes:
      before_body: "inc/google-analytics.js"
---

```{r setup, include=FALSE}
library(shiny)
library(shinyWidgets)
library(flexdashboard)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)
library(ggplot2)
library(plotly)
library(scales)
library(rlang)
library(DT)
library(RiHana)
```

```{r}

load("inc/funnel_data.RData")

#yesterdays_date<-Sys.Date()-1
#start_date<-lubridate::ceiling_date(yesterdays_date-271, unit="week",week_start = 1)

updatedFunnelViz <- reactive({

    currentToDate<-case_when(
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Week'~as.integer(lubridate::wday(lubridate::today(),week_start = 1)),
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Month'~as.integer(lubridate::mday(lubridate::today())),
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Quarter'~as.integer(lubridate::qday(lubridate::today())),
    TRUE~as.integer(100)
    )
  
  funnel_viz_data<-funnel_data %>% 
        mutate(hana_product_eval=case_when(
          input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
          input$FunnelSourceAttribution=='Blended'~hana_product,
          TRUE~'WrongAnswer'),
         report_date=case_when(
           input$FunnelGroupingDimension=='Cohort'~cohort_date,
           TRUE~funnel_date),
         report_week=case_when(
           input$FunnelGroupingDimension=='Cohort'~cohort_week,
           TRUE~funnel_week),
         report_month=case_when(
           input$FunnelGroupingDimension=='Cohort'~cohort_month,
           TRUE~funnel_month),
         report_quarter=case_when(
           input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
           TRUE~funnel_quarter),
         report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
         report_mtd=as.integer(lubridate::mday(report_date)),
         report_qtd=as.integer(lubridate::qday(report_date)),
        date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
         input$FunnelTimeDimension=='Month'~report_mtd,
         input$FunnelTimeDimension=='Quarter'~report_qtd
        )
      ) %>% 
    filter(measure!='marketing spend',
           report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
           !grepl(input$FunnelTours,measure,ignore.case = TRUE),                      
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    mutate(stage=factor(measure,levels =c("web_traffic","leads","opptys","tour_created","tour_scheduled","won"))) %>% 
    group_by(stage) %>% 
    summarise(values=sum(value)) %>% 
  mutate(percent=trunc(log(values)),
         conversion=scales::percent(values/lag(values)),
         plot_label=paste0(scales::comma(values),'<br>',conversion)) %>% 
  ungroup(.)  
  
 return(funnel_viz_data)
  
  })


updatedFunnelTable <- reactive({
  
    currentToDate<-case_when(
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Week'~as.integer(lubridate::wday(lubridate::today(),week_start = 1)),
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Month'~as.integer(lubridate::mday(lubridate::today())),
    input$FunnelTimeComplete== 'N' & input$FunnelTimeDimension=='Quarter'~as.integer(lubridate::qday(lubridate::today())),
    TRUE~as.integer(100)
    )

  table_data<-funnel_data %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           !grepl(input$FunnelTours,measure,ignore.case = TRUE),           
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city),
           date_length<=currentToDate) %>%
    mutate(measure=factor(measure,levels=c("marketing spend","web_traffic","leads","opptys","tour_created","tour_scheduled","won","deal_revenue")),
           timespan=case_when(
           input$FunnelTimeDimension=='Week'~report_week,
           input$FunnelTimeDimension=='Month'~report_month,
           input$FunnelTimeDimension=='Quarter'~report_quarter)) %>%
    group_by(measure,timespan) %>% 
    summarise(values=trunc(sum(value))) %>% 
        group_by(timespan) %>% 
    ungroup(.) %>% 
    complete(measure,timespan,fill=list(values=0)) %>% 
    pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    mutate(visit_conversion=leads/web_traffic,
           lead_to_oppty_conversion=opptys/leads,
           lead_to_won_conversion=won/leads) %>% 
    janitor::clean_names()

  # %>% 
  #   mutate(deal_revenue=scales::dollar(deal_revenue),
  #          visit_conversion=scales::percent(leads/web_traffic),
  #          lead_to_oppty_conversion=scales::percent(opptys/leads),
  #          lead_to_won_conversion=scales::percent(won/leads)) %>% 
  #   transform(`marketing spend`=scales::dollar(`marketing spend`))

  return(table_data)
})

updatedVisitConversionKPI<- reactive({
  
  kpi_data<-funnel_data %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
      TRUE~'WrongAnswer'
      )) %>% 
    filter(funnel_date>=input$FunnelTimeRange[1],
           funnel_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) 
  
  shiny::validate(
    shiny::need("web_traffic" %in% colnames(kpi_data), 
         "Tour conversion can't be calculated")
  )

  return(round((kpi_data$leads/kpi_data$web_traffic)*100,1))
  
}
)

updatedTourConversionKPI<- reactive({
  
  kpi_data<-funnel_data %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
      TRUE~'WrongAnswer'
      )) %>% 
    filter(funnel_date>=input$FunnelTimeRange[1],
           funnel_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) 
  
  shiny::validate(
    shiny::need("tour_scheduled" %in% colnames(kpi_data), 
         "Tour conversion can't be calculated")
  )

  return(round((kpi_data$tour_scheduled/kpi_data$leads)*100,1))
  
}
)

updatedWonConversionKPI<- reactive({
  
  kpi_data<-funnel_data %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
      TRUE~'WrongAnswer'
      )) %>% 
    filter(funnel_date>=input$FunnelTimeRange[1],
           funnel_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) 
  
  shiny::validate(
    shiny::need("won" %in% colnames(kpi_data), 
         "Won conversion can't be calculated")
  )

  return(round((kpi_data$won/kpi_data$leads)*100,1))
    
}
)

getUpdatedCPV<- reactive({
  
  cost_data<-funnel_data %>% 
    filter(measure %in% c('marketing spend', 'web_traffic')) %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    janitor::clean_names()

    shiny::validate(
    shiny::need("marketing_spend" %in% colnames(cost_data), 
         "There was no spend in this time range")
  )

  shiny::validate(
    shiny::need("web_traffic" %in% colnames(cost_data), 
         "There are no visits in this time range")
  )

  
  return(scales::dollar(cost_data$marketing_spend/cost_data$web_traffic))

}
)

getUpdatedCPL<- reactive({
  
  cost_data<-funnel_data %>% 
    filter(measure %in% c('marketing spend', 'leads')) %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    janitor::clean_names()

    shiny::validate(
    shiny::need("marketing_spend" %in% colnames(cost_data), 
         "There was no spend in this time range")
  )

  shiny::validate(
    shiny::need("leads" %in% colnames(cost_data), 
         "There are no leads in this time range")
  )

  
  return(scales::dollar(cost_data$marketing_spend/cost_data$leads))

}
)

getUpdatedCPT<- reactive({
  
  cost_data<-funnel_data %>% 
    filter(measure %in% c('marketing spend', 'tour_scheduled')) %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    janitor::clean_names()

    shiny::validate(
    shiny::need("marketing_spend" %in% colnames(cost_data), 
         "There was no spend in this time range")
  )

  shiny::validate(
    shiny::need("tour_scheduled" %in% colnames(cost_data), 
         "There are no tours in this time range")
  )

  
  return(scales::dollar(cost_data$marketing_spend/cost_data$tour_scheduled))

}
)

getUpdatedCPC<- reactive({
  
  cost_data<-funnel_data %>% 
    filter(measure %in% c('marketing spend', 'won')) %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    janitor::clean_names()

    shiny::validate(
    shiny::need("marketing_spend" %in% colnames(cost_data), 
         "There was no spend in this time range")
  )

  shiny::validate(
    shiny::need("won" %in% colnames(cost_data), 
         "There are no closed deals in this time range")
  )

  
  return(scales::dollar(cost_data$marketing_spend/cost_data$won))

}
)

getUpdatedROAS<- reactive({
  
  cost_data<-funnel_data %>% 
    filter(measure %in% c('marketing spend', 'deal_revenue')) %>% 
    mutate(hana_product_eval=case_when(
      input$FunnelSourceAttribution=='Explicit'~hana_product_orig,
      input$FunnelSourceAttribution=='Blended'~hana_product,
                 TRUE~'WrongAnswer'),
      report_date=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_date,
        TRUE~funnel_date),
      report_week=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_week,
        TRUE~funnel_week),
      report_month=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_month,
        TRUE~funnel_month),
      report_quarter=case_when(
        input$FunnelGroupingDimension=='Cohort'~cohort_quarter,
        TRUE~funnel_quarter),
      report_wtd=as.integer(lubridate::wday(report_date,week_start = 1)),
      report_mtd=as.integer(lubridate::mday(report_date)),
      report_qtd=as.integer(lubridate::qday(report_date)),
      date_length=case_when(
        input$FunnelTimeDimension=='Week'~report_wtd,
        input$FunnelTimeDimension=='Month'~report_mtd,
        input$FunnelTimeDimension=='Quarter'~report_qtd)
      ) %>%
    filter(report_date>=input$FunnelTimeRange[1],
           report_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product_eval,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product_eval),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    group_by(measure) %>% 
    summarise(values=sum(value)) %>% 
  pivot_wider(names_from = measure,
                values_from = values,
                values_fill=list(values=0)) %>% 
    janitor::clean_names()

    shiny::validate(
    shiny::need("marketing_spend" %in% colnames(cost_data), 
         "There was no spend in this time range")
  )

  shiny::validate(
    shiny::need("deal_revenue" %in% colnames(cost_data), 
         "There are no closed deals in this time range")
  )

  return(scales::dollar(cost_data$deal_revenue/cost_data$marketing_spend))

}
)


isr_summary_data<-reactive({
  updatedISR<-isr_activity_summary_edited %>% 
    filter(first_task_create_date>=input$FunnelTimeRange[1],
           first_task_create_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) 
  
  return(updatedISR)
})


getUpdatedISREngagements<- reactive({
  updatedISR<-isr_activity_detail_edited %>% 
    filter(engagement_date>=input$FunnelTimeRange[1],
           engagement_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    summarise(engagements=sum(engagements))
  
  return(updatedISR)
    
})


getUpdatedISROpptyConversion<- reactive({
  updatedISR<-isr_activity_summary_edited %>% 
    filter(first_task_create_date>=input$FunnelTimeRange[1],
           first_task_create_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    summarise(customers=n_distinct(contact_id),
              converters=length(contact_id[isr_review %in% c('Contacted, Tour Booked','Contacted, Closed Won')]),
              conversion=scales::percent(converters/customers),
              time_to_contact=round(mean(time_to_first_engagement,na.rm=TRUE),1),
              open_tasks=sum(num_tasks)-sum(completed_tasks))
  
  return(updatedISR)
    
})

updatedISRTrend <- reactive({
  

  trend_data <-isr_activity_detail_edited %>% 
    filter(engagement_date>=input$FunnelTimeRange[1],
           engagement_date<=input$FunnelTimeRange[2],
#           grepl(input$FunnelProduct,hana_product,ignore.case = TRUE),
            grepl(paste0(input$FunnelProduct,collapse="|"),hana_product),
            grepl(paste0(input$FunnelCity,collapse="|"),hana_city)) %>% 
    mutate(timespan=case_when(
           input$FunnelTimeDimension=='Week'~lubridate::floor_date(engagement_date,unit="week",week_start=1),
           input$FunnelTimeDimension=='Month'~lubridate::floor_date(engagement_date,unit="month"),
           input$FunnelTimeDimension=='Quarter'~lubridate::floor_date(engagement_date,unit="quarter"))) %>% 
    group_by(timespan,engagement_type) %>% 
    summarise(engagements=sum(engagements))

  return(trend_data)
})


observeEvent(input$helpBtn, {
#  show_alert(session, title = "Release Notes", text = paste0(readLines("inc/release_notes.md"),collapse="<br>"),html=TRUE)})
#    show_alert(title = "Release Notes", text = tags$body(paste0(readLines("inc/release_notes.md"),collapse='tags$br()'),html=TRUE))})
 showModal(modalDialog(
        title = "Release Notes",
        HTML(paste0(readLines("inc/release_notes.md"),collapse='<br>'))
 ))
})
```

Sidebar {.sidebar }
=====================================
###### **Data Updated:** _`r file.info('inc/funnel_data.RData')$mtime` ._

```{r}

  actionLink("helpBtn", "Notes")


dateRangeInput('FunnelTimeRange',
      label = 'Choose the time range',
      min=RiHana::get_relevant_date()$yoy_date,
      max=RiHana::get_relevant_date()$yesterdays_date,
      start = RiHana::get_relevant_date()$yoy_date, 
      end = RiHana::get_relevant_date()$yesterdays_date,
      weekstart = 1
    )


selectizeInput(
        'FunnelProduct', 'Choose a product', choices = unique(funnel_data$hana_product),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

selectizeInput(
        'FunnelCity', 'Choose a City', choices = na.omit(unique(funnel_data$hana_city)),
        options = list(
          placeholder = 'Please select an option below',
          onInitialize = I('function() { this.setValue("*"); }')
        ),
        multiple=TRUE
)

radioButtons("FunnelGroupingDimension",label="Pick how you want event dates to be related",
             choices=c("Cohort","Event"),
             inline=TRUE,
             selected="Cohort")
helpText("Note: Cohort means all events are tied to the Lead Creation date, Event means events use the actual event date")


radioButtons("FunnelTimeDimension",label="Pick the time interval",
             choices=c("Week","Month","Quarter"),
             selected="Month")
helpText("Note: Time interval specifies the X axis where appicable for trending data")

radioButtons("FunnelTimeComplete",label="Include in time range",
             choices=c("Full Range"="Y",
                       "To Date" = "N"),
             inline=TRUE)
helpText("Note: To Date will calculate all previous time dimensions to the same days complete as the current")


radioButtons("FunnelSourceAttribution",label="Choose Product attribution method",
             choices=c("Explicit","Blended"),
             inline=TRUE,
             selected="Blended")
helpText("Explicit link between product and metric vs. split for unknown product")

#these values are inverted because we are going to use the value to exclude
radioButtons("FunnelTours",label="View tours by date:",
             choices=c("Scheduled"="created",
                       "Created" = "scheduled"),
             inline=TRUE,
             selected = "created")


```

<strong>Marketing Spend</strong> - Dollars spent on major ad platforms (Google, Bing, Facebook, LinkedIn)

<strong>Web Traffic</strong> - Sessions as recorded in Google Analytics

<strong>Leads</strong> - Contacts created in Hubspot

<strong>Opportunities</strong> - Deals created in Hubspot

<strong>Tours</strong> - Hubspot meeting engagement where type = "Tour Scheduled"

<strong>Won</strong> - Hubspot deals where pipeline stage is "Closed Won"

Funnel Conversion {data-orientation=rows}
===================================== 

Row {data-height=100}
-------------------------------------

### Cost/Visitor

```{r}
renderValueBox({
updatedCPV <- getUpdatedCPV()
valueBox(prettyNum(updatedCPV,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#D2DEE0")
})
```

### Cost/Lead

```{r}
renderValueBox({
updatedCPL <- getUpdatedCPL()
valueBox(prettyNum(updatedCPL,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#D2DEE0")
})
```

### Cost/Tour

```{r}
renderValueBox({
updatedCPT <- getUpdatedCPT()
valueBox(prettyNum(updatedCPT,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#D2DEE0")
})
```

### Cost/Customer

```{r}
renderValueBox({
updatedCPC <- getUpdatedCPC()
valueBox(prettyNum(updatedCPC,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#D2DEE0")
})
```

### ROAS

```{r}
renderValueBox({
updatedROAS <- getUpdatedROAS()
valueBox(prettyNum(updatedROAS,big.mark = ","), 
         icon = "fa-file-invoice-dollar",
         color = "#D2DEE0")
})
```




Row {data-height=650}
-------------------------------------

### Funnel

```{r}

renderPlotly(
 {
   funnel_viz_data<-updatedFunnelViz()
   fig <- plot_ly() 
   fig <- fig %>%
   add_trace(type = "funnel",
            y = funnel_viz_data$stage,
            x = funnel_viz_data$percent,
            text=funnel_viz_data$plot_label,
            textposition = "inside",
            textinfo = "text",
            opacity = 0.65,
            marker = list(color = RiHana::hana_color_palette(n_distinct(funnel_viz_data$stage),1))) 
  
fig <- fig %>%
  layout(yaxis = list(categoryarray = funnel_viz_data$stage)) %>% 
  style(hoverinfo = 'none')

fig

    }
)

```

Row
-------------------------------------
### Visit to Lead

```{r}

renderGauge({
  VisitKPI<-updatedVisitConversionKPI()
gauge(VisitKPI, min = 0, max = 10, symbol = '%', gaugeSectors(
  success = c(5, 15), warning = c(2, 4), danger = c(0,2)
))
})
```

### Lead to Tour

```{r}
renderGauge({
  TourConversion<-updatedTourConversionKPI()
gauge(TourConversion, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(30, 100), warning = c(15, 30), danger = c(0,15)
))
})
```


### Lead to Closed Won

```{r}
renderGauge({
  WonConversion<-updatedWonConversionKPI()
gauge(WonConversion, min = 0, max = 25, symbol = '%', gaugeSectors(
  success = c(15, 25), warning = c(5, 15), danger = c(0,5)
))
})
```


Trends {data-orientation=rows}
===================================== 

Row {data-height=550}
-------------------------------------
### Trend Line

```{r}
sidebarPanel(
selectInput("FunnelMeasure", label = "Choose a metric",
            choices = c("Marketing Spend"="marketing_spend",
                        "Web Traffic"="web_traffic",
                        "Leads"="leads",
                        "Opportunities"="opptys",
                        "Tours"="tour_scheduled",
                        "Won"="won",
                        "Revenue"="deal_revenue",
                        "Visit Conversion"="visit_conversion",
                        "Lead/Oppty Conv"="lead_to_oppty_conversion",
                        "Lead/Won Conv"="lead_to_won_conversion"), 
            selected = c("web_traffic"),
            multiple = FALSE),
width=2
)
```


```{r}

renderPlotly({

    trend_dat<-updatedFunnelTable() %>% 
    rename(measure=!!rlang::sym(input$FunnelMeasure))
updatedFunnelTable
    plot_ly(trend_dat,
        marker = list(color = "#002636"),
        y = ~measure,
        x= ~timespan,
        type="bar") %>% 
     layout(xaxis=list(range = c(min(trend_dat$timespan),
                                 max(trend_dat$timespan))))

  })
```

Row 
-------------------------------------
### Table
```{r}
renderDataTable({
datatable(updatedFunnelTable() ,escape = FALSE,rownames = FALSE, extensions = c('Scroller', 'Buttons'), 
          options = c(list(scrollY = 200, scroller = TRUE),list(dom = 'tB',buttons = c('csv'))),fillContainer = T) %>% 
    formatCurrency(c('marketing_spend','deal_revenue'),digits=0) %>% 
    formatPercentage(c('visit_conversion','lead_to_oppty_conversion','lead_to_won_conversion'),1)
})
```

ISR Activity {data-orientation=rows}
===================================== 

Row {data-height=100}
-------------------------------------

### Assigned Contacts

```{r}
renderValueBox({
updatedISR <- getUpdatedISROpptyConversion()
valueBox(prettyNum(updatedISR$customers,big.mark = ","), 
         icon = "fa-address-card",
         color = "#D2DEE0")
})
```

### Open Tasks

```{r}
renderValueBox({
updatedISR <- getUpdatedISROpptyConversion()
valueBox(prettyNum(updatedISR$open_tasks,big.mark = ","), 
         icon = "fa-tasks",
         color = "#D2DEE0")
})
```


### Count of Engagement Activity

```{r}
renderValueBox({
updatedISR <- getUpdatedISREngagements()
valueBox(prettyNum(updatedISR$engagements,big.mark = ","), 
         icon = "fa-phone-volume",
         color = "#D2DEE0")
})
```

### Customer/Opportunity

```{r}
renderValueBox({
updatedISR <- getUpdatedISROpptyConversion()
valueBox(prettyNum(updatedISR$conversion,big.mark = ","), 
         icon = "fa-percent",
         color = "#D2DEE0")
})
```

### Avg Time to Contact (hours)

```{r}
renderValueBox({
updatedISR <- getUpdatedISROpptyConversion()
valueBox(prettyNum(updatedISR$time_to_contact,big.mark = ","), 
         icon = "fa-clock",
         color = "#D2DEE0")
})
```



Row {data-height=350}
-------------------------------------

### Engagement over time

```{r}

renderPlotly({
  trend_dat<-updatedISRTrend()

    plot_ly(trend_dat,
        y = ~engagements,
        x= ~timespan,
        color = ~engagement_type,
          colors=hana_color_palette(n_distinct(trend_dat$engagement_type),2),
          type="bar")%>%
      layout(barmode = "stack",
           bargap=0.1,
           legend = list(orientation = 'h'),
           xaxis=list(range = c(min(trend_dat$timespan),
                                 max(trend_dat$timespan))))


  })

```

Row {data-height=350}
-------------------------------------

### Time to First Task

```{r}

 renderPlotly({
   isr_tasks<-isr_summary_data()


isr_tasks %>% 
plot_ly(y = ~time_to_first_completed_task, 
        color = ~isr_review, 
        colors=hana_color_palette(n_distinct(isr_tasks$isr_review)),
        type = "box") %>% 
  layout(showlegend = FALSE)

 }
 )

```

### ISR Resolution

```{r}

 renderPlotly({
   isr_resolution<-isr_summary_data()


isr_resolution %>% 
  plot_ly(marker = list(color = "#002636"),
          orientation='h',
          y = ~isr_review,
#          bargroupgap=0.1,
#          bargap = 0.15,
          type="histogram")%>%
    highlight('plotly_click',color='red')

 }
 )

```


